title

### 2013-02-04 paper.tex
Added aquifer research

\section{Other Impacts}

@@

A secondary effect of high national connectivity is decreased reliance
on groundwater.

@@

As a result, we firmly recommend that the entirety of our proprosed
infrastructure developments, particularly the national pipeline network,
be implemented over the upcoming years.
\begin{thebibliography}{10}
\bibitem[1]{key-1}Cai, X., Cline, S., Rosegrant, M. (2002). Global Water
Outlook to 2025. \emph{International Food Policy Research Institute.}

\bibitem[2]{key-2}Estimated Use of Water in the United States County-Level
Data for 1985 (1955). \emph{US Geological Survey. }

\bibitem[3]{key-3}Estimated Use of Water in the United States County-Level
Data for 1990 (1990). \emph{US Geological Survey. }

\bibitem[4]{key-4}Estimated Use of Water in the United States County-Level
Data for 1995 (1995). \emph{US Geological Survey. }

\bibitem[5]{key-5}Estimated Use of Water in the United States County-Level
Data for 2000 (2000). \emph{US Geological Survey.}

\bibitem[6]{key-6}Estimated Use of Water in the United States County-Level
Data for 2005 (2005). \emph{US Geological Survey.}

\bibitem[7]{key-7}Per Capita Water Use. Retrieved February 1, 2013,
from http://www.pepps.fsu.edu/safe/pdf/sc1.pdf

\bibitem[8]{key-8}Loh, J. (n.d.). Water management: Learning from
Singapore's water succcess. Retrieved February 1, 2013, from http://workingwithwater.filtsep.com/view/934/water-management-learning-from-singapore-s-water-success/

\bibitem[9]{key-9}2013 USGS Budget Proposal. Retrieved February 1,
2013, from http://www.usgs.gov/newsroom/article.asp?ID=3103

\bibitem[10]{key-10}Moran, T. (2007). Water Wars: Quenching Las Vegas'
Thirst. Retrieved February 1, 2013, from http://abcnews.go.com/Nightline/story?id=3012250

\bibitem[11]{key-11}Mission 2012: Clean Water. Retrieved February
4, 2013, from http://web.mit.edu/12.000/www/m2012/finalwebsite/solution/glaciers.shtml

\bibitem[12]{key-12}City of Carlsbad Seawater Desalination, Retrieved
February 4, 2013, from http://www.carlsbadca.gov/services/departments/water/pages/seawaterdist.aspx

\bibitem[13]{key-13}US Drought Monitor. Retrieved February 3, 2013,
from http://droughtmonitor.unl.edu/

\bibitem[14]{key-14}South East Queensland water grid. Retrieved Februrary
3, 2013, from http://www.dsdip.qld.gov.au/infrastructure-delivery/south-east-queensland-water-grid.html

\bibitem[15]{key-15}Burian, S., Nix, S., Pitt, R., Durrans, S. (2000).
Urban Wastewater Management in the United States: Past, Present and
Future. Retrieved February 1, 2013, from http://www.sewerhistory.org/articles/whregion/urban\_wwm\_mgmt/urban\_wwm\_mgmt.pdf

\bibitem[16]{key-16}Kennedy, D., Klein, R., Clark, M. (2004) Use
and Effectiveness of Municipal Water Restrictions During Drought in
Colorado. Retrieved February 1, 2013, from http://sciencepolicy.colorado.edu/admin/publication\_files/resource-296-water\_restrictions\_jawra.pdf

\bibitem[17]{key-17}China's Three Gorges Dam. Retrieved February
3, 2013, from https://www.mtholyoke.edu/\textasciitilde{}vanti20m/classweb/website/environmentalimpact.html

\bibitem[18]{key-18}http://www.wunderground.com/blog/JeffMasters/article.html?entrynum=2326\end{thebibliography}

\end{document}

>>>>

\section{Environmental Impacts}

@@

A secondary and extremely desirable effect of high national connectivity is decreased reliance on groundwater. As a case study to understand the overexploitation of aquifers, consider the High Plains aquifer, which supplies water to Colorado, Kansas, Nebraska, New Mexico, Oklahoma, South Dakota, Texas, and Wyoming, some of the most agricultural states in the US \ref{key-19}.
Due to overexploitation many areas have experienced severe water-level decline, an average of 12.8 feet. While 9 percent of areas suffered decline as severe as 50 feet, only a bare 2 percent saw any significant (over 10 feet) of water-level rise since predevelopment. It is estimated that 9 percent of the total storage in this massive and essential groundwater supply was exhausted by 2005.

To alleviate this chronic and unsustainable drain on our nation's precious groundwater resources, our water grid would funnel water to agricultural states from more sustainable water supplies such as desalinated seawater and surface water supplies. At very least, we can guarantee spreading the stress on aquifers much more evenly than the current wildly varying rates of exploitation.

@@

As a result, we firmly recommend that the entirety of our proprosed
infrastructure developments, particularly the national pipeline network,
be implemented over the upcoming years.
\begin{thebibliography}{10}
\bibitem{key-1}Cai, X., Cline, S., Rosegrant, M. (2002). Global Water
Outlook to 2025. \emph{International Food Policy Research Institute.}

\bibitem{key-2}Estimated Use of Water in the United States County-Level
Data for 1985 (1955). \emph{US Geological Survey. }

\bibitem{key-3}Estimated Use of Water in the United States County-Level
Data for 1990 (1990). \emph{US Geological Survey. }

\bibitem{key-4}Estimated Use of Water in the United States County-Level
Data for 1995 (1995). \emph{US Geological Survey. }

\bibitem{key-5}Estimated Use of Water in the United States County-Level
Data for 2000 (2000). \emph{US Geological Survey.}

\bibitem{key-6}Estimated Use of Water in the United States County-Level
Data for 2005 (2005). \emph{US Geological Survey.}

\bibitem{key-7}Per Capita Water Use. Retrieved February 1, 2013,
from http://www.pepps.fsu.edu/safe/pdf/sc1.pdf.

\bibitem{key-8}Loh, J. (n.d.). Water management: Learning from
Singapore's water succcess. Retrieved February 1, 2013, from http://workingwithwater.filtsep.com/view/934/water-management-learning-from-singapore-s-water-success/.

\bibitem{key-9}2013 USGS Budget Proposal. Retrieved February 1,
2013, from http://www.usgs.gov/newsroom/article.asp?ID=3103.

\bibitem{key-10}Moran, T. (2007). Water Wars: Quenching Las Vegas'
Thirst. Retrieved February 1, 2013, from http://abcnews.go.com/Nightline/story?id=3012250.

\bibitem{key-11}Mission 2012: Clean Water. Retrieved February
4, 2013, from http://web.mit.edu/12.000/www/m2012/finalwebsite/solution/glaciers.shtml.

\bibitem{key-12}City of Carlsbad Seawater Desalination, Retrieved
February 4, 2013, from http://www.carlsbadca.gov/services/departments/water/pages/seawaterdist.aspx.

\bibitem{key-13}US Drought Monitor. Retrieved February 3, 2013,
from http://droughtmonitor.unl.edu/.

\bibitem{key-14}South East Queensland water grid. Retrieved Februrary
3, 2013, from http://www.dsdip.qld.gov.au/infrastructure-delivery/south-east-queensland-water-grid.html.

\bibitem{key-15}Burian, S., Nix, S., Pitt, R., Durrans, S. (2000).
Urban Wastewater Management in the United States: Past, Present and
Future. Retrieved February 1, 2013, from http://www.sewerhistory.org/articles/whregion/urban\_wwm\_mgmt/urban\_wwm\_mgmt.pdf.

\bibitem{key-16}Kennedy, D., Klein, R., Clark, M. (2004) Use
and Effectiveness of Municipal Water Restrictions During Drought in
Colorado. Retrieved February 1, 2013, from http://sciencepolicy.colorado.edu/admin/publication\_files/resource-296-water\_restrictions\_jawra.pdf.

\bibitem{key-17}China's Three Gorges Dam. Retrieved February
3, 2013, from https://www.mtholyoke.edu/\textasciitilde{}vanti20m/classweb/website/environmentalimpact.html.

\bibitem{key-18}http://www.wunderground.com/blog/JeffMasters/article.html?entrynum=2326.

\bibitem{key-19} V.L. McGuire. Changes in Water levels and Storage in the High Plains Aquifer, Predevelopment to 2005.

\end{thebibliography}
\end{document}
